Structuring College Access

### 2025-02-07 index.qmd
started presentation

---
title: 'Title'
subtitle: 'Subtitle'
author: ['Author', 'Author']
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

# Level-1 heading

@@

### Test map

@@

>>>>

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author:
  - name: Ozan Jaquette
    affiliation: UCLA
  - name: Karina Salazar
    affiliation: University of Arizona
  - name: Crystal Han
    affiliation: Stanford University
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

# Introduction

### Introduction
#### Talent is everywhere, but structure allocates talent to unequal opportunities

College Board "Geomarkets"

- Carve states and metropolitan areas into smaller geographic regions meant to define local recruiting markets

POP OUT OF GEOMARKETS

- Chicago
- New York

Geomarkets are an input to two College Board products

- Enrollment Planning Service:
- Student Search Service:

**Research questions** focus on metropolitan areas

1. What is SES and racial variation between, within geomarkets? How does this change over time?
1. What is SES and racial composition of included vs. excluded prospects, if student list purchases filter on particular Geomarkets?

### New York and Chicago Geomarkets

::: columns
::: {.column width="40%"}

![](./assets/images/nyc_geomarkets.png)
:::

::: {.column width="60%"}

![](./assets/images/chicago_geomarkets.png)
:::
:::

@@

# Empirical Context

# Theory
### Test map

@@

# Discussion
